Manuscript

### 2018-11-22 manuscript.Rmd
summary data/plots for write-up

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

Merged mutation calls (coding region, germline filtered):
```{r, eval=FALSE}
maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"

# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))

# Add Mutation_Status column
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wiltype", "Mutant")
maf_df <- unique(maf_df)
saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
```

@@

g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))

g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

Merge annotation data:
```{r, eval=FALSE}
# Melt CRISPR dataset for merging
crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
# Melt dependency probabilities dataset for merging
dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
# Merge dependency probabilities
crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
# Merge mutation annotations
maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr$Hugo_Symbol)))
crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
# Summarize number of mutant and Wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
# Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
# Add Color columns
crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
# Cell line lineages
crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
# Copy number
crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
# Gene expression (RPKM)
ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
```

```{r}
crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")

crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)

# Filter CRISPR for G2P genes in G2P
crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
```

@@

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")

crispr_signif_g2p_20gene <- as.character(crispr_signif_g2p_gene$Hugo_Symbol[0:20])

knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=7, fig.width=12}
crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_gene_color <- as.character(crispr_data_signif_g2p_gene$Color_Nonsilent)
names(crispr_data_signif_g2p_gene_color) <- crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")

crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))

crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
  labs(y = "CERES Score",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot

@@

```{r, eval=FALSE}
crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")

# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")

knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=15, fig.width=15}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
```

```{r}
crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")

@@

### G2P gene and drug
```{r}
test_ccle <- ccle_data_g2p_grid %>% group_by(Hugo_Symbol, Drug) %>% tally()
```

@@

```
for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))

write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
```

>>>>

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

Merged mutation calls (coding region, germline filtered):
```{r, eval=FALSE}
maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
# Add Mutation_Status column
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wildtype", "Mutant")
maf_df <- unique(maf_df)
saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
```

@@

g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

Merge annotation data:
```{r, eval=FALSE}
# Melt CRISPR dataset for merging
crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
# Melt dependency probabilities dataset for merging
dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
# Merge dependency probabilities
crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)

# Merge mutation annotations
maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
# Summarize number of mutant and Wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
# Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
# Add Color columns
crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)

# Cell line lineages
crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
# Copy number
crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
# Gene expression (RPKM)
ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
```

```{r}
crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)

# Filter CRISPR for G2P genes in G2P
crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
```

@@

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r}
unique(crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent)
```

```{r fig.height=7, fig.width=12}
crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% as.character(crispr_signif_g2p_gene$Hugo_Symbol))
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = as.character(crispr_signif_g2p_gene$Hugo_Symbol))

crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))

crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
  labs(y = "CERES Score",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot

@@

```{r, eval=FALSE}
crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=15, fig.width=15}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)

crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
```

```{r}
crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()

# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")

@@

```{r}
test_ccle <- ccle_data_g2p_grid %>% group_by(Hugo_Symbol, Drug) %>% tally()
```

@@

```
for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
```
